quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-07-06 paper-quollr.Rmd
Updated link plot colors

```{r linkerror, echo=TRUE, eval=knitr::is_html_output(), fig.cap="jkjio"}
show_link_plots(
  point_data = df_exe, 
  edge_data = trimesh
  )
```

@@

```{r, echo=TRUE, eval=knitr::is_html_output()}
show_error_link_plots(
  point_data = df_exe, 
  edge_data = trimesh
  )
```

>>>>

```{r linkerror, echo=TRUE, eval=knitr::is_html_output(), fig.cap="jkjio"}
show_link_plots(
  point_data = df_exe, 
  edge_data = trimesh, 
  point_colour = clr_choice
  )
```

@@

```{r, echo=TRUE, eval=knitr::is_html_output()}
show_error_link_plots(
  point_data = df_exe, 
  edge_data = trimesh, 
  point_colour = clr_choice
  )
```

### 2025-07-06 paper-quollr.tex
Updated link plot colors

\begin{verbatim}
show_link_plots(
  point_data = df_exe, 
  edge_data = trimesh
  )
\end{verbatim}

@@

\begin{verbatim}
show_error_link_plots(
  point_data = df_exe, 
  edge_data = trimesh
  )
\end{verbatim}

>>>>

\begin{verbatim}
show_link_plots(
  point_data = df_exe, 
  edge_data = trimesh, 
  point_colour = clr_choice
  )
\end{verbatim}

@@

\begin{verbatim}
show_error_link_plots(
  point_data = df_exe, 
  edge_data = trimesh, 
  point_colour = clr_choice
  )
\end{verbatim}
